YOSHIHIKO KUNISATO, Ph.D.

### 2021-07-24 articles.Rmd
update

@@

>>>>

### in press

- Hasegawa, A., Somatori, K., Nishimura, H., Hattori, Y., & Kunisato, Y. (in press). Depression, rumination, and impulsive action: A latent variable approach to behavioral impulsivity. The Journal of Psychology.

- Wang, K., Goldenberg, A., Dorison, C., Miller, J. K. P., Uusberg, A., Lerner, J. S., Gross, J., Marcu, G. M., Agadullina, E., Adamkovic, M., Roczniewska, M., Kassianos, A., Dursun, P., Arinze, A. I., Arinze, N. C., Ogbonnaya, C., Ndukaihe, I. L. G., Dalgar, I., Akkas, H., Macapagal, P. M. L., Lewis, S., Metin-Orta, I., Willis, M., Santos, A. C., Mokady, A., Reggev, N., Vasilev, M. R., Nock, N. L., Parzuchowski, M., Barría, M. E., Vranka, M. A., Ropovik, I., Yao, X., Becker, M., Manunta, E., Kaminski, G., Findor, A., Lewis, D. M. G., Aruta, J. J. B. R., Zickfeld, J., Vásquez, J. C., Pronizius, E., Lamm, C., Li, R., Valentova, J. V., Mioni, G., Cellini, N., Chen, S.-C., Moon, K., Azab, H., Todsen, A. L., van Schie, K., Bavolar, J., Warmelink, L., Ross, R. M., Stephen, I. D., Hostler, T., McCarthy, R. J., Grano, C., Singh Solorzano, C., Kácha, O., Arvanitis, A., Xiao, Q., Cárcamo, R., Zorjan, S., Tajchman, Z. J., Vilares, I., Pavlacic, J. M., Kunst, J. R., Tamnes, C. K., Atari, M., Sharifian, M., Hricova, M., Kačmár, P., Rahal, R.-M., Zakharov, I., Koehn, M. A., Esteban Serna, C., Hajdu, N., Calin-Jageman, R., Krafnick, A. J., Očovaj, S. B., Khosla, M., Urban, J., Boudesseul, J., Silva, J., Martončik, M., Šakan, D., Kuzminska, A., Djordjevic, J. M., Almeida, I. A. T., Lazarevic, L. B., Manley, H., Zambrano, D., Monteiro, R. P., Musser, E. D., Dunleavy, D. J., Godbersen, H., Ruiz-Fernandez, S., Reeck, C., Batres, C., Azevedo, F., Alvarez, D. S., Chen, Z., Verbruggen, F., Ziano, I., Tümer, M., Dubrov, D., Karababa, A., del Carmen, M., Aberson, C., Moller, A. C., Hubená, B., Ceary, C., Singer, G. A., Perillo, J. T., Ballantyne, T., Du, H., Pit, I. L., Hruška, M., Sousa, D., Aczel, B., Szaszi, B., Barzykowski, K., Micheli, L., Zsido, A. N., Paruzel-Czachura, M., Bialek, M., Kowal, M., Sorokowska, A., Misiak, M., Arriaga, P., Oliveira, R. A., Vaughn, L. A., Szwed, P., Kossowska, M., Kielińska, J., Antazo, B. G., Stieger, S., Nilsonne, G., simonovic, N., Taber, J. M., Gourdon-Kanhukamwe, A., Domurat, A., Ihaya, K., Yamada, Y., Urooj, A., Gill, T., Bylinina, L., Baklanova, E., Albayrak-Aydemir, N., Kappes, H. B., Gjoneska, B., House, T., Berkessel, J., Muda, R., Chopik, W. J., Çoksan, S., Seehuus, M., Khaoudi, A., Azouaghe, S., Arabi, K. A. E., Djamai, I., Wilson, J. P., Adiguzel, A., Kocalar, H. E., Norton, J., Papadatou-Pastou, M., Evans, K., Chuan-Peng, H., De la Rosa-Gomez, A., Ankushev, V., Bogatyreva, N., Grigoryev, D., Ivanov, A., Prusova, I., Romanova, M., Sarieva, I., Terskova, M., Hristova, E., Janak, A., Schei, V., Sverdrup, T. E., Askelund, A. D., Collins, W. M., Boucher, L., Ouherrou, N., Schrötter, J., Bokkour, A., Say, N., Sinkolova, S., Janjić, K., Stojanovska, D., Bijlstra, G., Mosannenzadeh, F., Reips, U.-D., Baskin, E., Ishkhanyan, B., Czamanski-Cohen, J., Dixson, B., Moreau, D., Sutherland, C., Noone, C., Anne, M., Janssen, S. M. J., Fu, C. H., Majeed, N. M., Kunisato, Y., Daches, S., Hartanto, A., Vdovic, M., Forbes, P., Kamburidis, J., Rachev, N. R., Stoyanova, A., Marinova, E., Schmidt, K., Suchow, J. W., Koptjevskaja-Tamm, M., Jernsäther, T., Olofsson, J., Bialobrzeska, O., Marszalek, M., Tatachari, S., Afhami, R., Law, W., Zuro, B., Van Doren, N., Soto, J., Searston, R. A., Miranda, J. F., Yeung, S. K., Krupić, D., Jaeger, B., Ren, D., Pfuhl, G., Klevjer, K., Vally, Z., Vargas-Nieto, J. C., Corral-Frías, N. S., Frias-Armenta, M., Lucas, M. Y., Torres, A. O., Toro, M., Vega, D., Solas, S. Á., Vilar, R., Massoni, S., Reyna, C., Pöntinen, S. J., Adetula, G. A., Foroni, F. P., Kurfali, M. A., Braun Kohlová, M., Harutyunyan, M., Landry, A. T., Ortiz, M., Voracek, M., Grinberg, M., Vintr, J., Kaliska, L., Pourafshari, R., Geiger, S. J., Beitner, J., Szala, A., Anjum, G., von Bastian, C. C., Cohen, N., Kirgizova, K., Muminov, A., Butt, M. M., Lee, J. M., Charyate, A., Sacakli, A., Richard, K., Cyrus-Lai, W., Fedotov, M., Wielgus, M., Adamus, S., Mola, D., Correa, P. S., Belaus, A., Muchembled, F., Ribeiro, R. R., Abbas, N., Čadek, M., Messerschmidt, J., Adetula, A., Kadreva, V., Bran, A., Vaidis, D. C., Vieira, L., Coelho, G. L. H., Whitt, C. M., Tullett, A. M., Du, X., Volz, L., Sarioguz, E., Korbmacher, M., Lima, T., Ribeiro, M. F. F., Verharen, J., Karekla, M., Jaremka, L. M., Storage, D., Studzinska, A., Hanel, P. H. P., Holford, D. L., Sirota, M., Wolfe, K., Chiu, F., Theodoropoulou, A., Ahn, E. R., Lin, Y., Westgate, E. C., Hofer, G., Vezirian, K., Travaglino, G. A., Marko, D., Li, M., Torunsky, N., Manavalan, M., Song, X., Walczak, R. B., Zdybek, P., Dalla Rosa, A., Kozma, L., Alves, S. G., Correia, R., Pinto, I. R., Babincak, P., Baník, G., Varella, M. A. C., Uttley, J., Beshears, J., Thommesen, K. K., Behzadnia, B., Bradford, M., Geniole, S., Silan, M. A., Vilsmeier, J. K., Tran, U. S., Morales-Izquierdo, S., Mensink, M. C., Groyecka-Bernard, A., Sorokowski, P., Radtke, T., Özdoğru, A. A., Ishii, T., Wichman, A. L., Röer, J. P., Ostermann, T., Davis, W. E., Suter, L., Ferreira, A., Agesin, B. B., Rana, K., Eudave, L., Campos, O., Grzech, K., Hausman Ozery, D., Jackson, E. A., Jimenez-Leal, W., Krizanic, V., Garcia, E. O. L., Drexler, S. M., Jurković, A. P., Štrukelj, E., Antoniadi, M., Desai, K., Gialitaki, Z., Kushnir, E., Nadif, K., Bravo, O. N., Nauman, R., Oosterlinck, M., Pantazi, M., Pilecka, N., Szabelska, A., van Steenkiste, I. M. M., Filip, K., Bozdoc, A. I., Westerlund, M., Ahlgren, L., Wang, C., Levy, N. L., Beaudry, J. L., Samojlenko, L., Isager, P. M., Chou, W., Pálfi, B., Schmidt, N.-D., Ortiz, M. V., Czarnek, G., Jones, M., Berkessel, J. B., Iyer, A., Parashar, N., Bundt, C., Pineda, L. M. S., Thomas, A. G., Kung, F. Y. H., Balci, B. B., Flowe, H. D., Topor, M., Yu, K., Anton-Boicuk, L., Kurfalı, M., Antfolk, J., Damnjanović, K., Hoyer, K., Galindo-Caballero, O. J., Calderón Pérez, L., Delgado, G. J., Frizzo, T., Capizzi, M., Greenburgh, A., Bosma, M., Karaarslan, C., Allred, T. B., Colloff, M. F., Karashiali, C., Sunami, N., Habib, S., Hassan, W., Brohmer, H., Dujols, O., Feldman, G., Ahmed, A., Bosch, J., Bai, H., Friedemann, M., Rojas-Berscia, L. M., Maturan, P. L. G., Walasek, L., Adoric, V. C., Carpentier, J., Joy-Gaba, J. A., Zabel, C., Ebersole, C. R., Chartier, C. R., Mallik, P. R., Urry, H. L., Buchanan, E. M., Coles, N. A., Primbs, M., Basnight-Brown, D., IJzerman, H., Forscher, P. S., & Moshontz, H., (in press). A multi-country test of brief reappraisal interventions on emotions during the COVID-19 pandemic. Nature Human Behaviour.

### 2021

- Shimono, Y., Hasegawa, A., Tsuchihara, K., Tanaka, K., Matsuda, Y., & Kunisato, Y.(2021) Longitudinal association between autistic traits and affinity for hikikomori in Japanese university students. Current Psychology. https://doi.org/10.1007/s12144-020-01287-x

- van Doorn, J., van den Bergh, D., Dablander, F., van Dongen, N., Derks, K., Evans, N., Gronau, Q., Haaf, J., Kunisato, Y., Ly, A., Marsman, M., Sarafoglou, A., Stefan, A., & Wagenmakers, EJ.(2011) Strong public claims may not reflect researchers’ private convictions. Significance, 18(1), 44-45.

@@

- Kato, A., Kunisato, Y., Katahira, K., Okimura, T., & Yamashita, Y. (2020) Computational Psychiatry Research Map (CPSYMAP): a New Database for Visualizing Research Papers. Frontiers in Psychiatry, 11, 1360.

### 2021-07-24 yoshihiko-kunisato.Rmd
update

## PERSONAL INFORMATION
####  Yoshihiko Kunisato
####  Associate Professor of Clinical Psychology
####  Department of Psychology,School of Human Sciences, SENSHU UNIVERSITY
####  DATE OF BIRTH: November 11, 1983
####  PLACE OF BIRTH: Hyougo Japan
####  CITIZENSHIP: Japanese
####  ADRESS: 2-1-1, Higashi-Mita, Tama, Kawasaki, 214-8580, JAPAN
####  E-MAIL: ykunisato (at sign) psy.senshu-u.ac.jp
####  [Google Scholar](http://scholar.google.com/citations?hl=en&user=cIhFY1YAAAAJ&view_op=list_works&gmla=AJsN-F7XXdjEVvO0pY8lFA19xtBq863U6a1bfQ12xa94TeIywgyckyZZLTHy4w22BKWLQJNyO9poNHdBCbXOlOjBAtMt007KIQvJ3pw1eoK3M-H7cbPbOmyU5ERgq4Wflfy8ZAjESXzV)
####  [Researchgate](https://www.researchgate.net/profile/Yoshihiko_Kunisato)

@@

## ACADEMIC APPOINTMENTS AND EMPLOYMENT
####  2009 – 2011 JSPS Research Fellowship for Young Scientists, Doctoral Course Students (DC1)
####  2011 - 2013 Research Associate,Faculty of Human Sciences, Waseda University
####  2013 -2015 Lecturer (with tenure),Faculty of Human Sciences, Senshu University
####  2015- Associate Professor, Faculty of Human Sciences, Senshu University

>>>>

## PERSONAL INFORMATION
####  Yoshihiko Kunisato
####  Professor of Clinical Psychology
####  Department of Psychology,School of Human Sciences, SENSHU UNIVERSITY
####  DATE OF BIRTH: November 11, 1983
####  PLACE OF BIRTH: Hyougo Japan
####  CITIZENSHIP: Japanese
####  ADRESS: 2-1-1, Higashi-Mita, Tama, Kawasaki, 214-8580, JAPAN
####  E-MAIL: ykunisato (at sign) psy.senshu-u.ac.jp
####  [Google Scholar](http://scholar.google.com/citations?hl=en&user=cIhFY1YAAAAJ&view_op=list_works&gmla=AJsN-F7XXdjEVvO0pY8lFA19xtBq863U6a1bfQ12xa94TeIywgyckyZZLTHy4w22BKWLQJNyO9poNHdBCbXOlOjBAtMt007KIQvJ3pw1eoK3M-H7cbPbOmyU5ERgq4Wflfy8ZAjESXzV)
####  [Researchgate](https://www.researchgate.net/profile/Yoshihiko_Kunisato)

@@

## ACADEMIC APPOINTMENTS AND EMPLOYMENT
####  2009 – 2011 JSPS Research Fellowship for Young Scientists, Doctoral Course Students (DC1)
####  2011 - 2013 Research Associate,Faculty of Human Sciences, Waseda University
####  2013 - 2015 Lecturer (with tenure),Faculty of Human Sciences, Senshu University
####  2015 - 2021 Associate Professor, Faculty of Human Sciences, Senshu University
####  2021 - Professor, Faculty of Human Sciences, Senshu University
